Verifying Demonstrations

### 2021-06-17 paper/protocol-trusted.tex
More clarifications to trusted protocol

Before Alice can have her participation in any event counted, she must get a 
certificate that ensures Sybil-freeness.
This is only done once\footnote{%
  It is repeated when the credential expires, in analogy to a passport in terms 
  of expected intervals.
}.
The keys can be reused for an arbitrary number of protests or, given
careful choices in the \ac{PRF} used for deriving identifiers, other
services that work with anonymous credentials.

@@

During the registration phase, each participant
generates a secret key~\((k, r)\) and
obtains a signature on it by the \ac{CA} \emph{but without revealing it} to the 
\ac{CA} (or to any part thereof in a decentralized \ac{CA} scenario).
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

Note that it does not matter if it is the witness or the protester who makes 
\(\psh\) available to the verifier.
The witness could compute \(\psh\) during the protest and give to the 
protester immediately, but we separate these steps to show that the witness can 
postpone those extra computations while potentially running on battery.

>>>>

Before Alice can have her participation in any event counted, she must get a 
certificate that ensures Sybil-freeness.
This is only done once\footnote{%
  It is repeated when the credential expires, in analogy to a passport that 
  must be renewed at regular intervals.
}.
The keys can be reused for an arbitrary number of protests or, given
careful choices in the \ac{PRF} used for deriving identifiers, other
services that work with anonymous credentials.

@@

During the registration phase, each participant
generates a secret key~\(\sk = (k, r)\) and
obtains a signature on it by the \ac{CA} \emph{but without revealing it} to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

Note that it does not matter if it is the witness or the protester who makes 
\(\psh\) available to the verifier.
The witness could compute \(\psh\) during the protest and give to the 
protester immediately, but we separate these steps to show that the witness can 
postpone those extra computations while potentially running on battery.
(Remember, the witness is assumed trusted.)
